Limits to Ecological Forecasting: Estimating Uncertainty for Critical Transitions with Deep Learning

### 2022-09-22 manuscript/manuscript.Rmd

```{r figure7}
#| fig.cap="Logs skill score over time. 
#|  Forecasts which underestimate uncertainty do substantially worse in logs score than in CRPS score. 
#|  Comparing this panel to those in Figure 6 highlights scenarios that most often underestimate uncertainty. 
#|  Generally, MCMC performs better relative to other models under this metric than it does under CRPS, 
#|  reflecting the bias-variance tradeoff taken when using biased estimators in machine learning."

>>>>

```{r figure7}
#| fig.cap="Logs skill score over time. 
#|  Forecasts which underestimate uncertainty do substantially worse in logs score than in CRPS score. 
#|  Comparing this panel to those in Figure 6 highlights scenarios that most often underestimate uncertainty. 
#|  Generally, MCMC performs better relative to other models under this metric than it does under CRPS, 
#|  reflecting the bias-variance tradeoff taken when using biased estimators in machine learning.
#|  The time axis in this plot and in Figure 6 refers to the time from the beginning of the forecast horizon, not the time from the beginning of the time series as in other plots."
